Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-07-26 ms.tex
Remove sub-section heading
Tone down a sentence

\subsection{Detection, and matched filter bank as a \ac{MLE}}

@@

The \ac{CRLB} is a useful analytical tool for predicting with what error an unknown parameter or parameters can be estimated from noisy observations. When an unbiased estimator exists, the \ac{CRLB} bound says that the covariance of the estimation error is bounded below by the Fisher information matrix. The \ac{CRLB} has been widely applied in \ac{GW} astronomy, for instance by \cite{fairhurst:2009} to predict the sky localization accuracy that is achievable with \ac{GW} observations. Here, we review the Fisher matrix calculation in \cite{fairhurst:2009} but add some physical interpretation to the particular structure of the covariance matrix.

>>>>

@@

The \ac{CRLB} is a useful analytical tool for predicting with what error an unknown parameter or parameters can be estimated from noisy observations. When an unbiased estimator exists, the \ac{CRLB} bound says that the covariance of the estimation error is bounded below by the Fisher information matrix. The \ac{CRLB} has been widely applied in \ac{GW} astronomy, for instance by \cite{fairhurst:2009} to predict the sky localization accuracy that is achievable with \ac{GW} observations. Here, we review the Fisher matrix calculation in \cite{fairhurst:2009} and discuss the interpretation.
